---
title: "p8106_hw5"
author: "Nathalie Fadel"
date: "4/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ISLR)
library(caret)
library(e1071)
```

###Part A
```{r}
data("OJ")

set.seed(1)
rowTrain <- sample(nrow(OJ), 800, replace = FALSE)
train_data <- OJ[rowTrain,]
test_data <- OJ[-rowTrain,]

set.seed(1)
svm_linear <- svm(Purchase ~ ., 
                  data = train_data,
                  kernel = 'linear',
                  cost = 0.01)
summary(svm_linear)

postResample(predict(svm_linear, train_data), train_data$Purchase)
postResample(predict(svm_linear, test_data), test_data$Purchase)

#Accuracy with training set: 83.37%
#Accuracy with testing set: 81.85%

ctrl <- trainControl(method = "cv", number = 10)

set.seed(1)
svml_fit <- train(Purchase~., 
                  data = train_data, 
                  method = "svmLinear2",
                  preProcess = c("center", "scale"),
                  tuneGrid = data.frame(cost = seq(0.01, 10, length.out = 20)),
                  trControl = ctrl)
svml_fit

postResample(predict(svml_fit, train_data), train_data$Purchase)
postResample(predict(svml_fit, test_data), test_data$Purchase)

#Accuracy of tuned model with training set: 84.25%
#Accuracy of tuned model with testing set: 81.85%

```

###Part B
```{r}
set.seed(1)
svm_radial <- svm(Purchase ~ ., 
                  data = train_data,
                  method = 'radial',
                  cost = 0.01)
summary(svm_radial)

postResample(predict(svm_radial, train_data), train_data$Purchase)
postResample(predict(svm_radial, test_data), test_data$Purchase)

#Accuracy with training set: 61.75%
#Accuracy with testing set: 58.89%

set.seed(1)
svm_radial_tune <- train(Purchase ~ ., 
                         data = train_data,
                         method = 'svmRadial',
                         trControl = ctrl,
                         preProcess = c('center', 'scale'),
                         tuneGrid = expand.grid(C = seq(0.01, 10, length.out = 20),
                                                sigma = 0.05691))
svm_radial_tune

postResample(predict(svm_radial_tune, train_data), train_data$Purchase)
postResample(predict(svm_radial_tune, test_data), test_data$Purchase)

#Accuracy of tuned model with training set: 85.63%
#Accuracy of tuned model with testing set: 82.59%

```

###Part C
As we can see from the above results, there was less of a difference in accuracy between the initial linear model and the tuned linear model. The radial models had a far greater difference between the initial and the tuned model.   
The final prediction accuracy with the linear model was 84.5% with training data, and 81.85% with the test set. The final prediction accuracy with the radial model was 85.63% and 82.59% with the test set. The radial model performs better by a small margin.




